oscar_figures

### 2021-03-18 oscar_figures.Rmd
Add supplementary iCLIP figure

>>>>

Supplementary iCLIP Figures

bars <- filtered_df %>%
  ungroup() %>%
  group_by(condition, pos) %>%
  mutate(mean_normalised = mean(normalised_counts),
         sd_normalised = sd(normalised_counts)) %>%
  mutate(colour = ifelse(condition == "H", healthy_colour, risk_colour))

bar_top <- ggplot(bars %>% filter(abs(pos-exon_snp) < 35), aes(x = pos, y = mean_normalised,
                                                       fill = colour)) +
  geom_bar(stat="identity", position="dodge") +
  scale_fill_identity() +
  geom_errorbar(aes(ymin = mean_normalised-sd_normalised, ymax=mean_normalised+sd_normalised),
                position="dodge") +
  geom_vline(xintercept = exon_snp, linetype="dashed") +
  ylab("XLs per 1000") +
  ggpubr::theme_pubr() +
  ggtitle("iCLIP signal around CE SNP") +
  xlab("")

bar_bottom <- ggplot(bars %>% filter(abs(pos-intron_snp) < 35), aes(x = pos, y = mean_normalised,
                                                       fill = colour)) +
  geom_bar(stat="identity", position="dodge") +
  scale_fill_identity() +
  geom_errorbar(aes(ymin = mean_normalised-sd_normalised, ymax=mean_normalised+sd_normalised),
                position="dodge") +
  geom_vline(xintercept = intron_snp, linetype="dashed") +
  ggpubr::theme_pubr() +
  ylab("XLs per 1000") +
  ggtitle("iCLIP signal around intronic SNP") +
  xlab("")

bar_combined <- bar_top / bar_bottom
bar_combined
